---
title: "Assignment 1"
author: "Ruixuan Ma"
date: "10/7/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Bootstrap Assignment 1: Due Sunday, 7 October at 23:59PM
*For help with Rmarkdown for reports, see this [white paper](http://www.stat.cmu.edu/~cshalizi/rmarkdown/#math-in-r-markdown) from Carnegie Mellon University's Department of Statistics and Data Science.*

### Part 1
Create a new GitHub repository called `BST650_Bootstrap`. Connect your computer to this repository. Create a `ReadMe.Rmd` file for this repository.

### Part 2
Create an Rmarkdown file called "Assignment1.Rmd". In this report:

1. Work through this lesson on functions: https://swcarpentry.github.io/r-novice-inflammation/02-func-R/
2. Create a function called `bootstrap()` that modifies the behaviour of the `sample()` function to perform a bootstrap sample on a given vector. Remember that bootstrap samples are the same **length** as the original sample, and remember that these samples are taken **with replacement** (*hint, hint*).
```{r}
dat <- read.csv(file = "/Users/maruixuan/Documents/Documents/GitHub/BST650_Bootstrap/inflammation-01.csv", header = FALSE)
bootstrap<-function(dat){sample(dat,40,replace=TRUE)}
```
3. Create the following vector: `grades = c(92, 80, 85, 95, 97, 78, 90, 86, 88, 66, 70, 82)`. Find the five-number summary, mean, and standard deviation of `grades`.
```{r}
grades <- c(92, 80, 85, 95, 97, 78, 90, 86, 88, 66, 70, 82)
summary(grades)
mean(grades)
sqrt(var(grades))
```
3. Call your function 10 times on `grades`. Store each bootstrapped sample as `boot1`, `boot2`, ..., `boot10`.
```{r}
boot1 <- c(bootstrap(grades))
boot2 <- c(bootstrap(grades))
boot3 <- c(bootstrap(grades))
boot4 <- c(bootstrap(grades))
boot5 <- c(bootstrap(grades))
boot6 <- c(bootstrap(grades))
boot7 <- c(bootstrap(grades))
boot8 <- c(bootstrap(grades))
boot9 <- c(bootstrap(grades))
boot10 <- c(bootstrap(grades))
```
4. Find the five-number summary, mean, and standard deviation of each bootstrap sample.

# For Boot1:
```{r}
summary(boot1)
mean(boot1)
sqrt(var(boot1))
```
# For Boot2:
```{r}
summary(boot2)
mean(boot2)
sqrt(var(boot2))
```
# For Boot3:
```{r}
summary(boot3)
mean(boot3)
sqrt(var(boot3))
```
# For Boot4:
```{r}
summary(boot4)
mean(boot4)
sqrt(var(boot4))
```
# For Boot5:
```{r}
summary(boot5)
mean(boot5)
sqrt(var(boot5))
```
# For Boot6:
```{r}
summary(boot6)
mean(boot6)
sqrt(var(boot6))
```
# For Boot7:
```{r}
summary(boot7)
mean(boot7)
sqrt(var(boot7))
```
# For Boot8:
```{r}
summary(boot8)
mean(boot8)
sqrt(var(boot8))
```
# For Boot9:
```{r}
summary(boot9)
mean(boot9)
sqrt(var(boot9))
```
# For Boot10:
```{r}
summary(boot10)
mean(boot10)
sqrt(var(boot10))
```
5. Create a data frame of these summary statistics (10 rows and seven columns).
```{r}
Boots <- data.frame(
BootID = c("boot1", "boot2", "boot3", "boot4", "boot5", "boot6", "boot7", "boot8", "boot9", "boot10"), 
Minimum = c(summary(boot1)[1], summary(boot2)[1], summary(boot3)[1], summary(boot4)[1],summary(boot5)[1], summary(boot6)[1], summary(boot7)[1], summary(boot8)[1], summary(boot9)[1], summary(boot10)[1]),
FirstQuantile = c(summary(boot1)[2], summary(boot2)[2], summary(boot3)[2], summary(boot4)[2],summary(boot5)[2], summary(boot6)[2], summary(boot7)[2], summary(boot8)[2], summary(boot9)[2], summary(boot10)[2]),
Median = c(summary(boot1)[3], summary(boot2)[3], summary(boot3)[3], summary(boot4)[3],summary(boot5)[3], summary(boot6)[3], summary(boot7)[3], summary(boot8)[3], summary(boot9)[3], summary(boot10)[3]),
Mean = c(summary(boot1)[4], summary(boot2)[4], summary(boot3)[4], summary(boot4)[4],summary(boot5)[4], summary(boot6)[4], summary(boot7)[4], summary(boot8)[4], summary(boot9)[4], summary(boot10)[4]),
ThirdQuantile = c(summary(boot1)[5], summary(boot2)[5], summary(boot3)[5], summary(boot4)[5],summary(boot5)[5], summary(boot6)[5], summary(boot7)[5], summary(boot8)[5], summary(boot9)[5], summary(boot10)[5]),
Maximum = c(summary(boot1)[6], summary(boot2)[6], summary(boot3)[6], summary(boot4)[6],summary(boot5)[6], summary(boot6)[6], summary(boot7)[6], summary(boot8)[6], summary(boot9)[6], summary(boot10)[6]),
StandardDeviation = c(sd(boot1), sd(boot2), sd(boot3), sd(boot4), sd(boot5), sd(boot6), sd(boot7), sd(boot8), sd(boot9), sd(boot10)),
stringsAsFactors = FALSE
)
```
6. Find the bootstrap estimate of each element of the five-number summary, mean, and standard deviation (look at the formula in your notes, then look at the `?colMeans` help file).
```{r}
bs_MeanOfMin <- colMeans(Boots[2])
bs_MeanOfQ1 <- colMeans(Boots[3])
bs_MeanOfQ2 <- colMeans(Boots[4])
bs_MeanOfMean <- colMeans(Boots[5])
bs_MeanOfQ3 <- colMeans(Boots[6])
bs_MeanOfMax <- colMeans(Boots[7])
bs_MeanOfSD <- colMeans(Boots[8])

nminus1Boots <- 10-1

bootMin1 <- ((Boots[c(1), c(2)]-bs_MeanOfMin)^2)/nminus1Boots
bootMin2 <- ((Boots[c(2), c(2)]-bs_MeanOfMin)^2)/nminus1Boots
bootMin3 <- ((Boots[c(3), c(2)]-bs_MeanOfMin)^2)/nminus1Boots
bootMin4 <- ((Boots[c(4), c(2)]-bs_MeanOfMin)^2)/nminus1Boots
bootMin5 <- ((Boots[c(5), c(2)]-bs_MeanOfMin)^2)/nminus1Boots
bootMin6 <- ((Boots[c(6), c(2)]-bs_MeanOfMin)^2)/nminus1Boots
bootMin7 <- ((Boots[c(7), c(2)]-bs_MeanOfMin)^2)/nminus1Boots
bootMin8 <- ((Boots[c(8), c(2)]-bs_MeanOfMin)^2)/nminus1Boots
bootMin9 <- ((Boots[c(9), c(2)]-bs_MeanOfMin)^2)/nminus1Boots
bootMin10 <- ((Boots[c(10), c(2)]-bs_MeanOfMin))^2/nminus1Boots
bootstrapMinSE <- bootMin1 + bootMin2 + bootMin3 + bootMin4 + bootMin5 + bootMin6 + bootMin7 + bootMin8 + bootMin9 + bootMin10
```